Carbonate chemistry at Ny-Ålesund

### 2021-12-23 awipev-CO2.Rmd
It knits!

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane and Bernard Gentili"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document: default
  word_document: default
  pdf_document: default
  odt_document: default
editor_options: 
  chunk_output_type: console
---
![ ](Images/AWIPEV-Logo.jpg){width=250px}

@@

d_all <- d_hour %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group = as.factor(dplyr::case_when(depth > 0 & depth <= 2 ~ '0-2',
                depth > 2 & depth <= 4 ~ '2-4',
                depth > 4 & depth <= 6 ~ '4-6',
                depth > 6 & depth <= 8 ~ '6-8',
                depth > 8 & depth <= 12 ~ '>8', #8 to 12.4
                TRUE ~ 'NA'
                )),
                sal_insitu_ctd_1m = ifelse(depth_group == '0-2', sal_insitu_ctd, NA),
                sal_insitu_ctd_3m = ifelse(depth_group == '2-4', sal_insitu_ctd, NA),
                sal_insitu_ctd_5m = ifelse(depth_group == '4-6', sal_insitu_ctd, NA),
                sal_insitu_ctd_7m = ifelse(depth_group == '6-8', sal_insitu_ctd, NA),
                sal_insitu_ctd_10m = ifelse(depth_group == '>8', sal_insitu_ctd, NA),
                temp_insitu_ctd_1m = ifelse(depth_group == '0-2', temp_insitu_ctd, NA),
                temp_insitu_ctd_3m = ifelse(depth_group == '2-4', temp_insitu_ctd, NA),
                temp_insitu_ctd_5m = ifelse(depth_group == '4-6', temp_insitu_ctd, NA),
                temp_insitu_ctd_7m = ifelse(depth_group == '6-8', temp_insitu_ctd, NA),
                temp_insitu_ctd_10m = ifelse(depth_group == '>8', temp_insitu_ctd, NA),
  ) %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    temp_insitu_ctd_1m,
    temp_insitu_ctd_3m,
    temp_insitu_ctd_5m,
    temp_insitu_ctd_7m,
    temp_insitu_ctd_10m
  )
), na.rm = TRUE)) %>% 
  ungroup()

@@

<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }
h3{ /* Header 3 */
  font-size: 22px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h4{ /* Header 4 */
  font-size: 18px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h5{ /* Header 5 */
  font-size: 16px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
</style>

# {.tabset .tabset-fade .tabset-pills}

@@

### **Introduction**
<div style="text-align: justify">  
The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory. It comprises two components: (1) continuous real-time measurements and (2) discrete measurements. The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.

### **AWIPEV Underwater Observatory**
<div style="text-align: justify">  
The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems. The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old pIer at 12 m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured. Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP for continuous measurements of currents and waves. Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations. The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter. During this time, the system is remotely controlled and maintained from Germany. All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed. The processed data are open access and available at http://codm.hzg.de/codm.

<div style="text-align:center" markdown="1">
  <img  src="./Images/Container.png" width="200" height="200">
  <img  src="./Images/Intake.png" width="200" height="200">
  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
</div>

### **Continuous and semi-continuous measurements**
<div style="text-align: justify">  
The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015. Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry. Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit. The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading. The sensor is the first instrument in the measuring loop; data are logged every minute. This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.

@@

### **Data availability**
The data at one minute frequency were tagged with the following quality flags

+ 1: good data
+ 3: failing the date and time test
+ 4: data not usable according to manufacturer
+ 6: failing the manufacturer range test (not used)
+ 7: failing the regional range test 
+ 12: failing the spike test (NAs from despike)
+ 13: failing the gradient test
+ 15: instrument not deployed or operated
+ 16: acid flush
+ 99: failing the final visual inspection

* Despike using oce::despike with n=2, k=5761

@@

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically. Salinity from FB is taken in consideration. If data gaps are encountered, they are filled with bottom salinity data from ctd (> 8 m). New column "sal_mix" is created and is the one used in ESSD paper.

+ 1 SBE45 inside the Ferrybox (sal_fb)
+ 5 CTD > 8 m depth (sal_insitu_ctd)

@@

df <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean10m = mean(sal_insitu_ctd_10m, na.rm = TRUE),
            range = mean(sal_insitu_ctd_1m, na.rm = TRUE) - mean(sal_insitu_ctd_10m, na.rm = TRUE)) %>% 
  ungroup()

p_sal_range <- ggplot(data = df) +
  geom_histogram((aes(x = range))) +
  labs(title = "Daily salinity difference between 1 and 10 m", x = "Difference") +
  Mytheme(size_labs = 8)
p_sal_range

kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
rm(sal_xts)
```
Extreme differences: `r dplyr::filter(df, range < -3 | range > 2)`.

There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m). The salinity difference between 1 and 10 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`). The difference with depth is therefore significant.

### **Sal FB / Sal CTD 10 m **

@@

## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
Temperature in situ at 11 m depth is taken in consideration. If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m). New column "temp_mix" is created. For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.

@@

### **Temperature profiles**
```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m)
temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("temp_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
dyLegend(show = "follow")   %>%
dyAxis("y",valueRange = c(-2, 10)) %>%
dyRangeSelector(height = 30, dateWindow= NULL)

df <- d_all %>% 
  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
            mean10m = mean(temp_insitu_ctd_10m, na.rm = TRUE),
            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_10m, na.rm = TRUE)) %>% 
  ungroup()
rm(temp_xts)
```
There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)`°C and `r max(df$range, na.rm=TRUE)`°C (mean: `r mean(df$range, na.rm=TRUE)`°C; `r median(df$range, na.rm=TRUE)`°C). The difference with depth is therefore significant.

### **T Ferrybox / T insitu 11 m **

@@

### **T 11 m / T CTD > 8 m **

@@

<!-- #### **TA since November 2018 (final installation)** -->
<!-- ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'} -->
<!--  # select subset of data and remove obvious outliers -->
<!--  at_nov_2018 <- -->
<!--   dplyr::select(d_all, datetime, at_calc, AT, at) %>% -->
<!--   filter(datetime > "2018-11-01", AT > 2250) -->
<!-- #despike -->
<!-- at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA")) -->
<!-- #plot -->
<!-- at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) + -->
<!--   geom_point(aes(y=AT, colour = "before"), size =3) + -->
<!--   geom_point(aes(y=AT_despike, colour = "after"), size = 2) + -->
<!--   labs(x = "Time", y = "Total alkalinity", color = "despike") -->
<!-- print(at_datetime) -->

<!-- at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA") -->
<!-- titre <- "Contros AT vs Calculated AT" -->
<!--  fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99) -->
<!-- ggreg2(fit, x = "at_calc", y = "AT_despike") -->

@@

## *p*CO~2~ and *f*CO~2~
The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015. It was deployed in the FerryBox with other sensors since July 2015, the 20th. A spare sensor (S/N: CO2FT-0515-001) was also bought in March 2015 and carried to Ny-Alesund to replace the first one in case of calibration or problem. Both sensors were set on a cycle according to informations given by Contros in March 2015 (c.kirbach@contros.eu):

@@

  - **Warm-up**: running without sending data. Done once, after the sensor is turned on. Time can vary depending on T water and power supply.
  - **Flushing**: running normally. Phase of equilibration that depends on the sensor configuration and the environment conditions. Warmer the water is and larger the flow is in front of the membrane, faster will be the response time and shorter will be the flush time. Recovery data of the sensor signal from the zeroing interval happen in this time. During this step the flush flag is set to “1” for simplifier extraction of the flush values.
  - **Measuring**: running normally and all other flags are on “0”. Sensor is fully equilibrated and T is stable.

@@

**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor. All data are normalized at in situ temperature. The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018). lmodel2: Model II Regression. R package version 1.7-3. https://CRAN.R-project.org/package=lmodel2

@@

pH is measured continuously by an autonomous seaFET pH sensor. Measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17 it was then measured once every minute. pH calibration is based on monthly, when possible, discrete samples collected at 11 m that were analysed with spectrophotometric method in Villefranche by Samir Alliouane. Measurments were performed several months after sampling. When sampling was not possible in the vicinity of the sensor for practical reasons (in winter), sampling was done in the harbour and is not taken in consideration for calibration for spatial reasons.  *Note that the pH sensor is mounted on a profiling structure. Here, in principle, only seaFET data recorded with a depth > 8 m should be taken into consideration.*

@@

Only 5 spectrophotometric pH which could be used for calibration when seaFET at > 8 m: 2018-11-16, 2019-04-17, 2019-10-11, 2020-01-27. All deployment meriods are covered but we had to alter the sampling time of:

* 2017-08-24 14:00 to 2017-08-24 19:00 (5 h later)
* 2017-11-28 09:00 to 2017-11-28 13:00 (4 h later)

@@

### **seaFET pHT calibrated**
Final calibrated seaFET pHT data (small green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).

@@

# split by depth
d_all <- d_all %>%
  dplyr::mutate(pHint_tot_sf_10m_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_10m = ifelse(depth >= 8 , pHint_tot_sf_10m, NA),
                depth_discrete = case_when(
                  !is.na(pHint_tot_sf_10m_1m) ~ 1,
                  !is.na(pHint_tot_sf_10m_3m) ~ 3,
                  !is.na(pHint_tot_sf_10m_5m) ~ 5,
                  !is.na(pHint_tot_sf_10m_7m) ~ 7,
                  !is.na(pHint_tot_sf_10m_10m) ~ 10
                  ),
                depth_discrete = as.factor(depth_discrete)
                )
d_all <- d_all %>% 
  dplyr::select(order(colnames(d_all)))

@@

“differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less.” (McLaughlin et al. 2017).

@@

 + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_10m, that is at depths deeper than 8 m.
  + pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, one should use data from 0 to 4 m.

@@

## Maintenance
<div style="text-align: justify">

>>>>

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane and Bernard Gentili"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document: default
  word_document: default
  pdf_document: default
  odt_document: default
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

![](Images/AWIPEV-Logo.jpg){width="250px"}

@@

d_all <- d_hour %>%
  dplyr::mutate_all(function(x)
    ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(
    depth_group = as.factor(
      dplyr::case_when(
        depth > 0 & depth <= 2 ~ '0-2',
        depth > 2 & depth <= 4 ~ '2-4',
        depth > 4 & depth <= 6 ~ '4-6',
        depth > 6 & depth <= 8 ~ '6-8',
        depth > 8 & depth <= 12 ~ '>8',
        #8 to 12.4
        TRUE ~ 'NA'
      )
    ),
    sal_insitu_ctd_1m = ifelse(depth_group == '0-2', sal_insitu_ctd, NA),
    sal_insitu_ctd_3m = ifelse(depth_group == '2-4', sal_insitu_ctd, NA),
    sal_insitu_ctd_5m = ifelse(depth_group == '4-6', sal_insitu_ctd, NA),
    sal_insitu_ctd_7m = ifelse(depth_group == '6-8', sal_insitu_ctd, NA),
    sal_insitu_ctd_10m = ifelse(depth_group == '>8', sal_insitu_ctd, NA),
    temp_insitu_ctd_1m = ifelse(depth_group == '0-2', temp_insitu_ctd, NA),
    temp_insitu_ctd_3m = ifelse(depth_group == '2-4', temp_insitu_ctd, NA),
    temp_insitu_ctd_5m = ifelse(depth_group == '4-6', temp_insitu_ctd, NA),
    temp_insitu_ctd_7m = ifelse(depth_group == '6-8', temp_insitu_ctd, NA),
    temp_insitu_ctd_10m = ifelse(depth_group == '>8', temp_insitu_ctd, NA),
  ) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(n_depth_ctd = sum(is.na(
    # create new variable to identify the hours for which there are CTD data at more than 1 depth
    c(
      temp_insitu_ctd_1m,
      temp_insitu_ctd_3m,
      temp_insitu_ctd_5m,
      temp_insitu_ctd_7m,
      temp_insitu_ctd_10m
    )
  ), na.rm = TRUE)) %>%
  ungroup()

@@

```{=html}
<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }
h3{ /* Header 3 */
  font-size: 22px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h4{ /* Header 4 */
  font-size: 18px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h5{ /* Header 5 */
  font-size: 16px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
</style>
```
#  {.tabset .tabset-fade .tabset-pills}

@@

### **Introduction**

<div style="text-align: justify">

The AWIPEV-CO2 project aims at starting the first time series for the
carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater
Observatory. It comprises two components: (1) continuous real-time
measurements and (2) discrete measurements. The rationale is that
discrete measurements are absolutely needed to calibrate and validate
the sensors.

### **AWIPEV Underwater Observatory**

<div style="text-align: justify">

The AWIPEV Underwater Observatory has been deployed at Ny-Alesund
(Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the
German Project COSYNA (Coastal Observation Systems of the Northern- and
Arctic Seas), which aims at increasing the availability of continuous
real-time data from remote but climatically-sensitive ecosystems. The
AWIPEV underwater observatory comprises a fully remote controlled
FerryBox system fed with seawater pumped in front of the old pIer at 12
m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a*
fluorescence are measured. Furthermore, an additional remote controlled
underwater sensor unit able to profile from 12 m to the surface at any
frequency carries additional sensors for salinity, pressure, turbidity,
oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP
for continuous measurements of currents and waves. Besides these
standard sensors, the underwater unit is equipped with a webcam and
stereo-optical device to remotely assess fish and jellyfish populations.
The AWIPEV observatory is specifically designed for polar experimental
work under extreme conditions including ice coverage and the
inaccessibility for about 7 months during polar winter. During this
time, the system is remotely controlled and maintained from Germany. All
data sampled by the sensors are continuously sent to a central server
system at Helgoland Island where the data are stored and processed. The
processed data are open access and available at
<http://codm.hzg.de/codm>.

::: {style="text-align:center" markdown="1"}
<img src="./Images/Container.png" width="200" height="200"/>
<img src="./Images/Intake.png" width="200" height="200"/>
<img src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200"/>
:::

### **Continuous and semi-continuous measurements**

<div style="text-align: justify">

The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon
Dioxyde partial pressure Flow Through surface water sensor) has been
installed in July 2015. Molecules of dissolved CO~2~ diffuse through a
thin composite membrane into the internal gas circuit leading to a
detector chamber, where the partial pressure of CO~2~ is determined by
means of infra-red absorption spectrometry. Concentration-dependent IR
light is converted into the output signal from calibration coefficients
stored in firmware and data from additional sensors within the gas
circuit. The measuring range is 200-1000 uatm, resolution is \< 1 uatm
and accuracy is +- 1% reading. The sensor is the first instrument in the
measuring loop; data are logged every minute. This instrument requires
yearly factory calibration; two sensors ara available to allow a
continuous time series.

@@

### **Data availability**

The data at one minute frequency were tagged with the following quality
flags

-   1: good data

-   3: failing the date and time test

-   4: data not usable according to manufacturer

-   6: failing the manufacturer range test (not used)

-   7: failing the regional range test

-   12: failing the spike test (NAs from despike)

-   13: failing the gradient test

-   15: instrument not deployed or operated

-   16: acid flush

-   99: failing the final visual inspection

-   Despike using oce::despike with n=2, k=5761

@@

## Salinities

Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically. Salinity from FB is taken in consideration. If
data gaps are encountered, they are filled with bottom salinity data
from ctd (> 8 m). New column "sal_mix" is created and is the one used in
ESSD paper.

-   1 SBE45 inside the Ferrybox (sal_fb)
-   5 CTD > 8 m depth (sal_insitu_ctd)

@@

tmp <- d_all %>% 
  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
            mean10m = mean(sal_insitu_ctd_10m, na.rm = TRUE),
            range_diff = mean(sal_insitu_ctd_1m, na.rm = TRUE) - mean(sal_insitu_ctd_10m, na.rm = TRUE)) %>% 
  ungroup()

p_sal_range <- ggplot(data = tmp) +
  geom_histogram((aes(x = range_diff))) +
  labs(title = "Daily salinity difference between 1 and 10 m", x = "Difference") +
  Mytheme(size_labs = 8)
print(p_sal_range)

kable(quantile(x = tmp$range_diff, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
rm(sal_xts)
```

```{r, eval=FALSE, echo=FALSE}
Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.

There are `r sum(!is.na(tmp$range_diff))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).

The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm=TRUE)` and `r max(tmp$range_diff, na.rm=TRUE)` (mean: `r mean(tmp$range_diff, na.rm=TRUE)`; `r median(tmp$range_diff, na.rm=TRUE)`). The difference with depth is therefore significant.
```

### **Sal FB / Sal CTD 10 m**

@@

## Temperatures

Several temperature sensors are on site, 1 inside the Ferrybox (SBE45),
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically and 1 fixed at 11 m depth (sbe38). Temperature in
situ at 11 m depth is taken in consideration. If data gaps are
encountered, they are filled with bottom temperature data from ctd (> 8
m). New column "temp_mix" is created. For the moment, no gaps are
encountered and temp_mix = temp_insitu_11m.

@@

### **Temperature profiles**

```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m)
temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("temp_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
dyLegend(show = "follow")   %>%
dyAxis("y",valueRange = c(-2, 10)) %>%
dyRangeSelector(height = 30, dateWindow= NULL)

tmp <- d_all %>% 
  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m) %>%
  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
  group_by(date) %>% 
  summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
            mean10m = mean(temp_insitu_ctd_10m, na.rm = TRUE),
            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_10m, na.rm = TRUE)) %>% 
  ungroup()
rm(temp_xts)
```

There are `r sum(!is.na(tmp$range))` days with temperature values at
both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
and 9 m ranges between `r min(tmp$range, na.rm=TRUE)`°C and
`r max(tmp$range, na.rm=TRUE)`°C (mean:
`r mean(tmp$range, na.rm=TRUE)`°C; `r median(tmp$range, na.rm=TRUE)`°C).
The difference with depth is therefore significant.

### **T Ferrybox / T insitu 11 m**

@@

### **T 11 m / T CTD \> 8 m**

@@

<!-- #### **TA since November 2018 (final installation)** -->

<!-- ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'} -->

<!--  # select subset of data and remove obvious outliers -->

<!--  at_nov_2018 <- -->

<!--   dplyr::select(d_all, datetime, at_calc, AT, at) %>% -->

<!--   filter(datetime > "2018-11-01", AT > 2250) -->

<!-- #despike -->

<!-- at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA")) -->

<!-- #plot -->

<!-- at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) + -->

<!--   geom_point(aes(y=AT, colour = "before"), size =3) + -->

<!--   geom_point(aes(y=AT_despike, colour = "after"), size = 2) + -->

<!--   labs(x = "Time", y = "Total alkalinity", color = "despike") -->

<!-- print(at_datetime) -->

<!-- at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA") -->

<!-- titre <- "Contros AT vs Calculated AT" -->

<!--  fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99) -->

<!-- ggreg2(fit, x = "at_calc", y = "AT_despike") -->

@@

## *p*CO~2~ and *f*CO~2~

The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros
(Germany) in February 2015. It was deployed in the FerryBox with other
sensors since July 2015, the 20th. A spare sensor (S/N: CO2FT-0515-001)
was also bought in March 2015 and carried to Ny-Alesund to replace the
first one in case of calibration or problem. Both sensors were set on a
cycle according to informations given by Contros in March 2015
([c.kirbach\@contros.eu](mailto:c.kirbach@contros.eu){.email}):

@@

-   **Warm-up**: running without sending data. Done once, after the
    sensor is turned on. Time can vary depending on T water and power
    supply.
-   **Flushing**: running normally. Phase of equilibration that depends
    on the sensor configuration and the environment conditions. Warmer
    the water is and larger the flow is in front of the membrane, faster
    will be the response time and shorter will be the flush time.
    Recovery data of the sensor signal from the zeroing interval happen
    in this time. During this step the flush flag is set to "1" for
    simplifier extraction of the flush values.
-   **Measuring**: running normally and all other flags are on "0".
    Sensor is fully equilibrated and T is stable.

@@

**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2
measured using a Contros sensor. All data are normalized at in situ
temperature. The black dotted line is the 1:1 line while the blue solid
line shows the line obtained by a major axis regression (Legendre, 2018-
Pierre Legendre (2018). lmodel2: Model II Regression. R package version
1.7-3. <https://CRAN.R-project.org/package=lmodel2>

@@

pH is measured continuously by an autonomous seaFET pH sensor.
Measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17
it was then measured once every minute. pH calibration is based on
monthly, when possible, discrete samples collected at 11 m that were
analysed with spectrophotometric method in Villefranche by Samir
Alliouane. Measurments were performed several months after sampling.
When sampling was not possible in the vicinity of the sensor for
practical reasons (in winter), sampling was done in the harbour and is
not taken in consideration for calibration for spatial reasons. *Note
that the pH sensor is mounted on a profiling structure. Here, in
principle, only seaFET data recorded with a depth \> 8 m should be taken
into consideration.*

@@

Only 5 spectrophotometric pH which could be used for calibration when
seaFET at \> 8 m: 2018-11-16, 2019-04-17, 2019-10-11, 2020-01-27. All
deployment meriods are covered but we had to alter the sampling time of:

-   2017-08-24 14:00 to 2017-08-24 19:00 (5 h later)
-   2017-11-28 09:00 to 2017-11-28 13:00 (4 h later)

@@

### **seaFET pHT calibrated**

Final calibrated seaFET pHT data (small green dots) are shown here after
calibration with spectro measurements (red dots) according to each
period of deployement, defined between 2 spectro measurements (shading
grey).

@@

# split by depth
d_all <- d_all %>%
  dplyr::mutate(pHint_tot_sf_10m_1m = ifelse(depth_group == '0-2', pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_3m = ifelse(depth_group == '2-4', pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_5m = ifelse(depth_group == '4-6', pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_7m = ifelse(depth_group == '6-8', pHint_tot_sf_10m, NA),
                pHint_tot_sf_10m_10m = ifelse(depth_group == '>8', pHint_tot_sf_10m, NA)#,
                # depth_discrete = case_when(
                #   !is.na(pHint_tot_sf_10m_1m) ~ 1,
                #   !is.na(pHint_tot_sf_10m_3m) ~ 3,
                #   !is.na(pHint_tot_sf_10m_5m) ~ 5,
                #   !is.na(pHint_tot_sf_10m_7m) ~ 7,
                #   !is.na(pHint_tot_sf_10m_10m) ~ 10
                #   ),
                # depth_discrete = as.factor(depth_discrete)
                )
d_all <- d_all %>% 
  dplyr::select(order(colnames(d_all)))

@@

"differences between calibrated sensor pH values and values obtained
from discrete, check samples can be expected to be as small as 0.02 pH
units, and perhaps less." (McLaughlin et al. 2017).

@@

-   To compare with pCO2/pCO2 measured in the Ferrybox seems therefore
    better to stick with pH_10m, that is at depths deeper than 8 m.
-   pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes,
    one should use data from 0 to 4 m.

@@

## Maintenance

<div style="text-align: justify">

### **REMOS**
